---
title: "Misinformation analysis for 7AAVDM59 week 7 seminar A"
author: "Daniel Allington"
date: "2024-03-07"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)

options(scipen = 999)

misinfo_d <- read_csv('../data/life-under-lockdown-wave2-extract.csv')
```

```{r}
misinfo_d %>%
  ggplot(aes(x = beliefs)) +
  geom_histogram(bins = 6)
```

```{r}
misinfo_d %>%
  ggplot(aes(x = gender)) +
  geom_bar()
```

# Association between gender and number of misinformation beliefs
```{r}
misinfo_d %>%
  filter(gender %in% c('Female', 'Male')) %>%
  t.test(formula = beliefs ~ gender, data = .)
```

In the sample, males had more misinformation beliefs (0.73) than females (0.61), but Welch's two sample t-test confirms that this difference was not statistically significant, t(484.31) = -1.201, p = 0.230.

# Association between age and number of misinformation beliefs
## Hypothesis
We expect a positive correlation between age and number of misinformation beliefs.

## Methodology
To test the hypothesis, the product-moment coefficient of correlation between age and number of misinformation beliefs was calculated.

## Findings
```{r}
misinfo_d %>%
  ggplot(aes(x = age, y = beliefs)) +
  geom_jitter()
```

```{r}
misinfo_d %>%
  cor.test(
    formula = ~ age + beliefs, data = ., method = 'pearson')
```

There is a statistically significant moderate negative correlation between age and number of misinformation beliefs, r(498) = -.24, p < .001.

# Association between reliance on Facebook for information about coronavirus and number of misinformation beliefs
## Hypothesis
We expect a positive correlation between amount of knowledge about coronavirus which comes from Facebook and number of misinformation beliefs.

## Methodology
To test the hypothesis, the rank-order coefficient of correlation between amount of knowledge about coronavirus and number of misinformation beliefs was calculated.

## Findings
```{r}
misinfo_d <- misinfo_d %>%
  mutate(
    know_facebook_coded = know_facebook %>%
      recode(
        "Nothing at all" = 0,
        "Not very much" = 1,
        "A fair amount" = 2,
        "A great deal" = 3
      )
  )

misinfo_d %>%
  cor.test(
    formula = ~ know_facebook_coded + beliefs, data = ., method = 'spearman')
```

There was a statistically significant positive rank-order correlation between amount of knowledge about coronavirus from Facebook and number of misinformation beliefs, rs(498) = .23, p < .001.

# Association between age and misinformation beliefs, controlling for reliance on Facebook for information
```{r}
misinfo_d <- misinfo_d %>%
  mutate(
    know_facebook_binary = as.numeric(know_facebook_coded == 3)
  )

misinfo_d %>%
  lm(
    formula = beliefs ~ age + know_facebook_binary, data = .
  )

```


